Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2023-02-10 src/tex/ms.tex
Add sentence related to previous citation

We find that the progenitor properties and even the ability to produce a
GW150914-like merger event is strongly correlated with hyperparameter settings;
different assumptions about the black hole masses at merger in GW150914 imply
wildly different formation channels and ZAMS progenitor masses for this event
and some nearby combinations of ZAMS masses are unable, with any reasonable
hyperparameter settings, to produce a DCO merger like GW150914.  We further
exhibit preliminary results of an ongoing analysis over the entire GWTC-3
catalog \citep{GWTC-3} that suggest that the accretion efficiency in stable mass
transfer may depend non-trivially on the primary black hole mass in merging
systems; our methodology allows for a systematic study of such dependencies,
which we will explore more fully in future work.

>>>>

We find that the progenitor properties and even the ability to produce a
GW150914-like merger event is strongly correlated with hyperparameter settings,
consistent with results from prior forward modeling studies cited above;
different assumptions about the black hole masses at merger in GW150914 imply
wildly different formation channels and ZAMS progenitor masses for this event
and some nearby combinations of ZAMS masses are unable, with any reasonable
hyperparameter settings, to produce a DCO merger like GW150914.  We further
exhibit preliminary results of an ongoing analysis over the entire GWTC-3
catalog \citep{GWTC-3} that suggest that the accretion efficiency in stable mass
transfer may depend non-trivially on the primary black hole mass in merging
systems; our methodology allows for a systematic study of such dependencies,
which we will explore more fully in future work.
